---
title: "Readme"
output: html_document
Author: Ivan Andreu Rascon 
---

---
output: html_document
---
# Manipulate the dataframe as necessary so that you can calculate average duration, f0 and intensity as a function of lexical stress (extra points if you can create a plot)


## Load library
```{r}
library(tidyverse)
```

## Read data into R
```{r}
read_csv("data/data.csv")
```


## Creation of the object with the CSV file
```{r}
my_data <- read_csv("data/data.csv")
```


## Mean duration
```{r}
mean(my_data$durationV)
```


## Mean f0
```{r}
mean(my_data$f0)
```


## Mean intensity
```{r}
mean(my_data$int)
```

## Summary
```{r}
my_data %>% 
  summarize(dur_avg = mean(durationV), f0_avg = mean(f0), int_avg = mean(int))
```

Por alguna razón me redondea los números aquí 



## Separate variable Info into different columns (word, stress)
```{r}
separate(data = my_data, col = info, into = c("word", "stress"), sep = "_")
```


## Assign it to an object
```{r}
my_new_data <- separate(data = my_data, col = info, into = c("word", "stress"), sep = "_")
```


## Means by lexical stress

### Means of durationV for stress 1 and 2 
```{r}
my_new_data %>%
  group_by(stress) %>%
  summarize(mean_durationV = mean(durationV))
```



## Plots
  No se si esto esta bien
  
### Plot of f0 and stress
  

```{r}
my_data %>% 
  separate(., col = info, into = c("item", "stress"), sep = "_") %>%
  ggplot(., aes(x = stress, y = f0, color = item)) +
    geom_point() 
```

### Plot of intensity and stress

```{r}
my_data %>% 
  separate(., col = info, into = c("item", "stress"), sep = "_") %>%
  ggplot(., aes(x = stress, y = int, color = item)) +
    geom_point() 
```


### Plot of intensity and stress

```{r}
my_new_data %>%
  ggplot(., aes(x = stress, y = int, col = "orange"))+
  geom_point()
```


### Not sure what am I doing

```{r}
plot(x = my_data$f0 , y = my_data$int, type = 'o', xlab = "f0", ylab = "intensity", col = "orange")
```


```{r}
plot(x = my_new_data$f0 , y = my_new_data$int, type = 'o', xlab = "f0", ylab = "intensity", col = "green")
```

```{r}
plot(x = my_new_data$durationV , y = my_new_data$int, type = 'o', xlab = "f0", ylab = "intensity", col = "green")
```


```{r}
hist(my_data$f0, 
     main="f0", 
     xlab="f0", 
     ylab = "count",
     border="black", 
     col="blue",
     xlim=c(90,115),
     las=2, 
     breaks=10)
```


